---
title: "Report of metadynamics generated by metadynminer and rmarkdown"
output: 
  pdf_document:
    toc: false
    number_sections: false
documentclass: article
classoption:
  - portrait
  - a4paper
---

HILLS file was loaded and summary was printed
```{r}
hillsf<-read.hills("HILLS", per=c(T,T))
summary(hillsf)
```
\newpage

Free energy surface was calculated and plotted:
```{r fig.width=8, fig.height=8}
fesf<-fes(hillsf)
plot(fesf)
```
\newpage

Free energy surface with scale was plotted:
```{r fig.width=8, fig.height=7}
plot(fesf, colscale=T)
```
\newpage

Free energy minima were identified and plotted:
```{r fig.width=8, fig.height=8}
minimf<-fesminima(fesf)
summary(minimf)
plot(minimf)
```
\newpage

Free energy profiles were evaluated, convergence was assessed
on the second half of the simulation and plotted.

```{r fig.width=8, fig.height=6}
proff<-feprof(minimf)
summary(proff, imind=hillsf$size[1]/2)
plot(proff)
```
\newpage

One dimensional free energy profile was calculated along CV1 and
its evolution was plotted:
```{r fig.width=8, fig.height=6}
fesf<-fes2d21d(hillsf, remdim=2)
plot(fesf-min(fesf), lwd=4, col="black")
for(i in 1:9) {
  tfes1<-fes2d21d(hillsf, remdim=2, imax=i*hillsf$size[1]/10)
  lines(tfes1-min(tfes1), col=rainbow(13)[i])
}
```
\newpage

One dimensional free energy profile was calculated along CV2 and
its evolution was plotted:
```{r fig.width=8, fig.height=6}
fesf<-fes2d21d(hillsf, remdim=1)
plot(fesf-min(fesf), lwd=4, col="black")
for(i in 1:9) {
  tfes1<-fes2d21d(hillsf, remdim=1, imax=i*hillsf$size[1]/10)
  lines(tfes1-min(tfes1), col=rainbow(13)[i])
}
```

